%\subsection{Terminology}
%
%\begin{itemize}[noitemsep]
%  \item Users.
%  Programmers who use SimpleChubby user-level interfaces to write a user-defined synchronization service.
%  \item Servers.
%  SimpleChubby service runs on a set of processes called servers.
%  \item Clients.
%  A user-written program runs on a process called a client, which connects to the server
%  and cooperates with the server to implement SimpleChubby lock service.
%  \item Leader server.
%  One of servers is responsible for processing requests from the clients, and coordinates other servers.
%  \item Follower server.
%  The servers other than the leader servers.
%\end{itemize}

SimpleChubby implementation consists of a client library linked to user programs,
and a server executable running on each server.
When user code invokes the client library interfaces to access files or perform locking operations,
the client library performs corresponding remote procedure calls to the leader server,
waits for replies from the leader server, and returns the result back to the user.

\subsubsection{Client side}
The client library offers a set of interfaces for users to access SimpleChubby lock service,
and talks with the leader server to implement the interfaces. 

User code does not talk with the leader server directly since the client library
needs to know what requests are issued so that it can help a leader server
to recover lost states during a server fail-over.
Meanwhile, the client library can do certain sanity checks before sending requests
to the leader server.

The client library also cooperates with the servers to achieve server fail-over.  
It tries to connect to a new leader server once the old one fails,
and help the new server recover such lost states
as open files, registered events, and lock waiting queues
using client side information.

\subsubsection{Server side}

SimpleChubby runs a group of servers to provide a reliable lock service.

A server can run as the leader server or as a follower server,
as decided by a consensus protocol.
When running as a follower server, it serves as a replica to duplicate critical
operations happening on the leader server, and prepares to be promoted to a leader server.
When running as a leader server, it accepts and processes requests from clients.
The leader server also monitors client failures, and clears its states after failure,
i.e., reclaiming its holding locks after a certain timeout.

The leader server maintains two categories of states.
The first category of states includes lock ownership and file system content. These
states are made persistent, and accesses or changes to them go through a consensus protocol.
The second category of states includes active client lists,
open files, registered events, and lock waiting queues.
Theses states can be recovered with the help of clients,
and thus are not persistent and does not go through a consensus protocol.

SimpleChubby does not make all the leader server states persistent by a consensus protocol,
because it takes too much overhead to maintain all the states,
but certain states can be easily recovered
using client side information.
